A sheaf--function dictionary for algebraic tori over local fields

### 2013-09-24 shanghai.tex
Changes to sections 3 and 4

\begin{definition}\label{def:QC}
A \emph{quasicharacter sheaf on $G$} is a triple
$\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is a rank one $\ell$-adic local system on $\bG$
-- a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component; 
\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$
  is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
%
  \[
  \begin{tikzcd}[row sep=30]
  \bm_3^*\gqcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
    &&  \bm^*\gqcs{L} \boxtimes \gqcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
    \gqcs{L} \boxtimes \bm^* \gqcs{L} \arrow{rr}{\id \boxtimes \mu}
    &&  \gqcs{L} \tight{0}{\boxtimes}{0} \LxL
  \end{tikzcd}
  \]
%
\labitem{(CS.2)}{CS.2} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
%
  \[
  \begin{tikzcd}[row sep=20]
  \Frob{\GxxG}^* \bm^* \gqcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
    && \Frob{\GxxG}^*(\LxL)\\
    \arrow[equal]{u} \bm^*  \Frob{G}^* \gqcs{L} \arrow[swap]{d}{\bm^* \phi}
    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
    \bm^*\gqcs{L} \arrow{rr}{\mu}
    && \LxL
  \end{tikzcd}
  \]
\end{enumerate}
\end{definition}

@@

\begin{proof}
  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
  $\bf^*\gqcs{L}$ is a local system of rank~$1$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
  connected component and let $i$ be the image of $j$ under the group
  homomorphism $\pi_0(\bf) : \pi_0(\bH) \to \pi_0(\bG)$.
  Write $d_i : \bG^i \hookrightarrow \bG$ for
  the inclusion of $\bG^i$ and $\bf^j : \bH^j \to \bG^i$
  for the restriction of $f$ to $\bH^j$.  Since $\gqcs{L}$ is locally constant on the connected
  components of $\bG$, there is a finite \'etale covering
  $a_i : X_i \to \bG^i$ such that $a_i^* (\gqcs{L}\vert_{\bG^i})$
  is constant. Let $b_j : Y_j \to \bH^j$ be the
  pull-back of $a_i$ along $\bf^j$ and let $g_j : Y_j \to X_i$ be
  the map opposite $\bf^j$. Then $b_j$ is a finite \'etale covering
  of $\bH^j$ and
  \[
  b_j^* \left( (\bf^* \gqcs{L})\vert_{\bH^j}\right)
  = (\bf\circ c_j \circ b_j)^*\gqcs{L}
  = (d_i\circ a_i\circ g_j)^*\gqcs{L} = g_j^* a_i^* (\gqcs{L}\vert_{\bG^i}).
  \]

  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf, its pullback
  $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$ along $g_j$ is also constant.
  Thus $\bf^*\gqcs{L}$ is locally constant on
  $\bH^j$. Since $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$ for every
  geometric point ${\bg}$ on $\bG$, and since $\gqcs{L}$ has
  rank $1$ on connected components of $\bG$, it follows that
  $f^*\gqcs{L}$ also has rank $1$ on connected components of $\bG$.
  This completes the proof that $\bf^*\gqcs{L}$ satisfies condition \ref{CS.0}.

@@

  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.3} allows the application
  of $f^*$ to morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback
  $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
%
  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
  commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
  hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
  the hypothesis that $X$ is locally of finite type over $\Fq$.

@@

Consider the short exact sequence in the category of $\QC$-schemes
defining the component group scheme for $G$:
\begin{equation}\label{eq:pi0}
\begin{tikzcd}
0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
\end{tikzcd}
\end{equation}
Since $\pi_0(G)$ is also a $\QC$-scheme, 
Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines a sequence of functors
\[
\begin{tikzcd}
\QC(0) \rar & \QC(\pi_0(G)) \rar & \QC(G) \rar & \QC(G^0) \rar & \QC(0)
\end{tikzcd}
\]
which induces, upon passage to isomorphism classes of objects, a sequence of group homomorphisms 
\[
\begin{tikzcd}
\QCiso{0} \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & \QCiso{0}.
\end{tikzcd}
\]
It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected} and  we will find $\QCiso{G^0}$
and $\QCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
the snake lemma will then allow us to show
\[
\QCiso{G} \iso G(\Fq)^*,%\Hom_\text{grp}(G(\Fq),\EE^\times),
\]
canonically.
%\section{Products} 
We end this section with a simple result on products of quasicharacter sheaves,
which is needed to show that the isomorphism above is functorial.

\begin{proposition}\label{prop:product}
The rule $\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
\[
\QC(G_1)\times (G_2) \to \QC(G_1\times G_2)
\]
(categorical product on the left, product of group schemes over $\Fq$ on the right) and 
\[
\begin{tikzcd}[column sep=60]
\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
& \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
(G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
\end{tikzcd}
\]
commutes.
\end{proposition}

\begin{proof}
The only non-trivial part is essential surjectivity. Set $G \ceq G_1\times G_2$.
Let $\qcs{L}$ be a quasicharacter sheaf on $G$. Define $f : G\to G\times G$
by $f(g_1,g_2) \ceq (g_1,e_2,e_1,g_2)$. Observe that $m\circ f = \id_G$. 
Let $p_1$, $p_2$ be the projection morphisms pictured below:
\[
\begin{tikzcd}
G & \arrow[swap]{l}{p_1} G\times G \arrow{r}{p_2} & G.
\end{tikzcd}
\]
Then the isomorphism $\mu : m^* \gqcs{L} \to \gqcs{L}\boxtimes \gqcs{L}$ gives an isomorphism
\[
f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}.
\]
Let $r_1$ and $r_2$ be the projection morphisms pictured below, with sections $q_1$, $q_2$, also morphisms of group schemes:
\[
\begin{tikzcd}
G_1  \arrow[swap, bend right]{r}{q_1} &
\arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &
\arrow[bend left]{l}{q_2} G_2.
\end{tikzcd}
\]
Then $p_1\circ f = r_1 \circ q_1$ and $f_2 = r_2\circ f$, 
so $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$. 
Now $\qcs{L}_1 \ceq r_1^* \qcs{L}$ is a quasicharacter sheaf on $G_1$ 
and $\qcs{L}_2 \ceq r_2^* \qcs{L}$ is a quasicharacter sheaf on $G_2$, 
by Proposition~\ref{prop:pullback}. 
Then 
\[
f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L} = r_1^*\gqcs{L}_1\otimes r_2^* \gqcs{L}_2 = \gqcs{L}_1\boxtimes \gqcs{L}_2.
\]
In this way, $\mu$ determines an isomorphism
\[
f^*\mu : \gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2.
\]
So $\boxtimes$ is essentially surjective.
\end{proof}

@@

When using quasicharacter sheaves to study characters, it is useful to understand
how quasicharacter sheaves behave under change of fields.
Let $k'$ be a finite extension of $k$. Then $k\to k'$ induces a group homomorphism
$i_{k'/k} : G(k) \hookrightarrow G(k')$ which, in turn, gives
\begin{align*}
i_{k'/k}^* : G(k')^* &\to G(k)^* \\
\chi &\mapsto \chi\circ i_{k'/k}.
\end{align*}
We can interpret this operation on characters in terms of quasicharacter sheaves, as follows.
%

@@

In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
\begin{align*}
\Nm^* : G(k)^* &\to G(k')^* \\
\chi &\mapsto \chi\circ \Nm.
\end{align*}
We can also interpret this operation on characters in terms of quasicharacter sheaves, as follows.

@@

\begin{proposition}\label{prop:basechange}
 The rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$ 
 defines a monoidal functor $\QC(G) \to \QC(G_{k'})$. 
 Moreover, the following diagram commutes, 
 where the top map is induced by $\QC(G) \to \QC(G_{k'})$ 
 and the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
\[
\begin{tikzcd}[column sep=60]
\QCiso{G} \rar{\nu_{k'/k}} \dar{\trFrob{G}} & \QCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
G(k)^*  \rar{\Nm^*} & G(k')^*.
\end{tikzcd}
\]
\end{proposition}
\begin{proof}
Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and $x \in G(k')$ and write $\Frob{}$ for $\Frob{G}$.
We may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
\Clifton{Please note what I did here.}
and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
Applying \ref{CS.2} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
\[
\begin{tikzcd}
\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{\Frob{}(x)} \otimes \gqcs{L}_{\Frob{}^2(x)} \otimes \cdots \otimes \gqcs{L}_x
\dar{\phi_x \otimes (\Frob{}^*\phi)_x \otimes \cdots \otimes ((\Frob{}^{n-1})^*\phi)_x} \\
\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{\Frob{}(x)} \otimes \cdots \otimes \gqcs{L}_{\Frob{}^{n-1}(x)}.
\end{tikzcd}
\]
Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$, mapping to $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
along the bottom map, where $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.1}, $v$ maps to
$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
Let $\alpha_i \in \EEx$ represent $((\Frob{}^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
\end{proof}

Finally, let $G'$ be a $\QC$-scheme over $k'$;
we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
\[
(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
\]
Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes 
\[
G' \hookrightarrow (\Res_{k'/k}G')_{k'}
\]
mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing pullback
along this map with $\nu_{k'/k}$ from Proposition~\ref{prop:basechange} yields a functor
\[
\QC(\Res_{k'/k}G') \to \QC(G').
\]

\begin{proposition}
The following diagram of isomorphisms commutes, where the bottom map is the identity:
\[
\begin{tikzcd}
\QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \rar & \QCiso{G'} \dar{\trFrob{G'}}\\
G'(k')^* \rar & G'(k')^*
\end{tikzcd}
\]
\end{proposition}
\begin{proof}
By Proposition~\ref{prop:pullback} the pullback part of the definition corresponds to the map $(\Res_{k'/k}G')(k') \to G'(k')^*$
induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on $(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'$
is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
\end{proof}

>>>>

\begin{definition}\label{def:QC}
A \emph{quasicharacter sheaf on $G$} is a triple
$\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is a rank one $\ell$-adic local system on $\bG$
-- a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component; 
\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$ \David{We should explain the $\boxtimes$ notation}
  is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
%
  \[
  \begin{tikzcd}[row sep=30]
  \bm_3^*\gqcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
    &&  \bm^*\gqcs{L} \boxtimes \gqcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
    \gqcs{L} \boxtimes \bm^* \gqcs{L} \arrow{rr}{\id \boxtimes \mu}
    &&  \gqcs{L} \tight{0}{\boxtimes}{0} \LxL
  \end{tikzcd}
  \]
%
\labitem{(CS.2)}{CS.2} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
%
  \[
  \begin{tikzcd}[row sep=20]
  \Frob{\GxxG}^* \bm^* \gqcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
    && \Frob{\GxxG}^*(\LxL)\\
    \arrow[equal]{u} \bm^*  \Frob{G}^* \gqcs{L} \arrow[swap]{d}{\bm^* \phi}
    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
    \bm^*\gqcs{L} \arrow{rr}{\mu}
    && \LxL
  \end{tikzcd}
  \]
\end{enumerate}
\end{definition}

@@

\begin{proof}
  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
  $\bf^*\gqcs{L}$ is a local system of rank~$1$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
  connected component and let $d_i : \bG^i \hookrightarrow \bG$ be the image of $j$ under the group
  homomorphism $\pi_0(\bf) : \pi_0(\bH) \to \pi_0(\bG)$.  Write $\bf^j : \bH^j \to \bG^i$
  for the restriction of $f$ to $\bH^j$.  Since $\gqcs{L}$ is locally constant on the connected
  components of $\bG$, there is a finite \'etale covering
  $a_i : X_i \to \bG^i$ such that $a_i^* (\gqcs{L}\vert_{\bG^i})$
  is constant.  Define $Y_j$ in the following diagram through pullback:
  \[
  \begin{tikzcd}[row sep=20, column sep=30]
   Y_j \dar[dashed]{g_j} \rar[dashed]{b_j} & \bH^j \dar{\bf^j} \rar[hook]{c_j} & \bH \dar{\bf} \\
   X_i \rar{a_i} & \bG^i \rar[hook]{d_i} & \bG
  \end{tikzcd}
  \]
  Then $b_j$ is a finite \'etale covering
  of $\bH^j$ and
  \[
  b_j^* \left( (\bf^* \gqcs{L})\vert_{\bH^j}\right)
  = (\bf\circ c_j \circ b_j)^*\gqcs{L}
  = (d_i\circ a_i\circ g_j)^*\gqcs{L} = g_j^* a_i^* (\gqcs{L}\vert_{\bG^i}).
  \]

  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf, its pullback
  $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$ along $g_j$ is also constant.
  Thus $\bf^*\gqcs{L}$ is locally constant on
  $\bH^j$. Since $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$ for every
  geometric point ${\bg}$ on $\bG$, and since $\gqcs{L}$ has
  rank $1$ on connected components of $\bG$, it follows that
  $f^*\gqcs{L}$ also has rank $1$ on connected components of $\bG$.
  \David{can't we just say rank 1?  Why ``on connected components of $G$?"}
  This completes the proof that $\bf^*\gqcs{L}$ satisfies condition \ref{CS.0}.

@@

  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.3} defines the action
  of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback in schemes,
  $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
%
  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
  commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
  hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
  the hypothesis that $X$ is locally of finite type over $\Fq$.

@@

Consider the short exact sequence in the category of $\QC$-schemes
defining the component group scheme for $G$:
\begin{equation}\label{eq:pi0}
\begin{tikzcd}
0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
\end{tikzcd}
\end{equation}
Since $\pi_0(G)$ is also a $\QC$-scheme, 
Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines a sequence of functors
\[
\begin{tikzcd}
\QC(0) \rar & \QC(\pi_0(G)) \rar & \QC(G) \rar & \QC(G^0) \rar & \QC(0)
\end{tikzcd}
\]
which induces a sequence of group homomorphisms 
\[
\begin{tikzcd}
\QCiso{0} \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & \QCiso{0}.
\end{tikzcd}
\]
after passing to isomorphism classes.  It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected}, \ref{sec:etale} and \ref{sec:etalecohom} we will find $\QCiso{G^0}$
and $\QCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
the snake lemma will then allow us to show that
\[
\QCiso{G} \iso G(\Fq)^*.
\]

%\section{Products}

We end this section with a simple result on products of quasicharacter sheaves,
which is needed to show that the isomorphism above is functorial.

\begin{proposition}\label{prop:product}
If $G_1$ and $G_2$ are $\QC$-schemes, the rule $\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
\[
\QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
\]
and 
\[
\begin{tikzcd}[column sep=60]
\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
& \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
(G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
\end{tikzcd}
\]
commutes.
\end{proposition}

\begin{proof}
The only non-trivial part is essential surjectivity. Set $G \ceq G_1\times G_2$
and write $e_1$ and $e_2$ for the identity elements of $G_1$ and $G_2$.
Let $\qcs{L}$ be a quasicharacter sheaf on $G$. Define $f : G\to G\times G$
by $f(g_1,g_2) \ceq (g_1,e_2,e_1,g_2)$. Observe that $m\circ f = \id_G$. 
Let $p_1$, $p_2$ be the projection morphisms pictured below:
\[
\begin{tikzcd}
G & \arrow[swap]{l}{p_1} G\times G \arrow{r}{p_2} & G.
\end{tikzcd}
\]
Then the isomorphism $\mu : m^* \gqcs{L} \to \gqcs{L}\boxtimes \gqcs{L}$ gives an isomorphism
\[
f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}.
\]
Let $r_1$ and $r_2$ be the projection morphisms pictured below, with sections $q_1$ and $q_2$, also morphisms of group schemes:
\[
\begin{tikzcd}
G_1  \arrow[swap, bend right]{r}{q_1} &
\arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &
\arrow[bend left]{l}{q_2} G_2.
\end{tikzcd}
\]
Then $p_1\circ f = q_1 \circ r_1$ and $p_2 \circ f = q_2\circ r_2$, 
so $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$. 
Now $\qcs{L}_1 \ceq q_1^* \qcs{L}$ is a quasicharacter sheaf on $G_1$ 
and $\qcs{L}_2 \ceq q_2^* \qcs{L}$ is a quasicharacter sheaf on $G_2$, 
by Proposition~\ref{prop:pullback}. 
Then 
\[
f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L} = r_1^*\gqcs{L}_1\otimes r_2^* \gqcs{L}_2 = \gqcs{L}_1\boxtimes \gqcs{L}_2.
\]
In this way, $\mu$ determines an isomorphism
\[
f^*\mu : \gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2.
\]
So $\boxtimes$ is essentially surjective. \David{Don't we also need to note that $f^*\mu$ is compatible with the rational structures?}
\end{proof}

@@

When using quasicharacter sheaves to study characters, it is useful to understand
how quasicharacter sheaves behave under change of fields.
Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
\begin{align*}
i_{k'/k}^* : G(k')^* &\to G(k)^* \\
\chi &\mapsto \chi\circ i_{k'/k}.
\end{align*}
We can interpret this operation on characters in terms of quasicharacter sheaves:
%

@@

In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
\begin{align*}
\Nm^* : G(k)^* &\to G(k')^* \\
\chi &\mapsto \chi\circ \Nm.
\end{align*}
We can also interpret this operation on characters in terms of quasicharacter sheaves.

@@

\begin{proposition}\label{prop:basechange}
 The rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$ 
 defines a monoidal functor $\QC(G) \to \QC(G_{k'})$. 
 Moreover, the following diagram commutes:
\[
\begin{tikzcd}[column sep=60]
\QCiso{G} \rar{\nu_{k'/k}} \dar{\trFrob{G}} & \QCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
G(k)^*  \rar{\Nm^*} & G(k')^*.
\end{tikzcd}
\]
\end{proposition}
\begin{proof}
Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $\Frob{}$ for $\Frob{G}$.  For any $x \in G(k')$,
we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
\Clifton{Please note what I did here.}
and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
Applying \ref{CS.2} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
\[
\begin{tikzcd}
\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{\Frob{}(x)} \otimes \gqcs{L}_{\Frob{}^2(x)} \otimes \cdots \otimes \gqcs{L}_x
\dar{\phi_x \otimes (\Frob{}^*\phi)_x \otimes \cdots \otimes ((\Frob{}^{n-1})^*\phi)_x} \\
\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{\Frob{}(x)} \otimes \cdots \otimes \gqcs{L}_{\Frob{}^{n-1}(x)}.
\end{tikzcd}
\]
Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.1}, $v$ maps to
$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
Let $\alpha_i \in \EEx$ represent $((\Frob{}^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
\end{proof}

Finally, let $G'$ be a $\QC$-scheme over $k'$;
we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
\[
(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
\]
Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes 
\[
G' \hookrightarrow (\Res_{k'/k}G')_{k'}
\]
mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$ 
from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
\[
\rho : \QC(\Res_{k'/k}G') \to \QC(G').
\]

\begin{proposition}
The following diagram of isomorphisms commutes, where the bottom map is the identity:
\[
\begin{tikzcd}
\QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\trFrob{G'}}\\
G'(k')^* \rar & G'(k')^*
\end{tikzcd}
\]
\end{proposition}
\begin{proof}
By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map $(\Res_{k'/k}G')(k') \to G'(k')^*$
induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on $(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'$
is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
\end{proof}
